Taking Dyads Seriously

### 2018-03-02 paper/netsMatter.tex
app edits
abstract

\small{\singlespacing{
\begin{abstract}
	Much of international relations scholarship concerns dyads: dyadic hypotheses and especially dyadic data. Yet, contemporary research brushes aside the complications that come with analyzing interdependent relational data. Dyadic observations do not typically satisfy the conditional independence criterion required for many statistical approaches. As a result, studies often produce results with biased coefficient estimates and poorly calibrated standard errors. These biases have profound consequences for evaluating parametric models. We present an alternative, regression-based approach that accounts for the dependencies complicating this type of analysis. We first present a simulation exercise highlighting the model's ability to account for the dependencies that emerge in relational data. In addition, we replicate three recent studies in recent international relations scholarship, and compare  the standard approach to our alternative. For each study, we find that conventional methods overstate the effect of key variables in the study of interstate conflict (and trade), underestimate the uncertainty in these effects, and in some cases lead researchers to faulty conclusions about the statistical significance and substantive importance of their variables. Further, we show that our approach dominates in terms of out-of-sample cross-validations, rendering it more useful in forecasting applications and for  modeling the data generating process behind outcomes of interest.
\end{abstract}
}}

@@

%\bibliography{/Users/maxgallop/documents/whistle/master}
\bibliography{/Users/s7m/whistle/master}
 % \bibliography{/Users/mdw/Git/whistle/master}
% \bibliography{/Users/cassydorff/ProjectsGit/master}
% \bibliographystyle{authordate1}
\bibliographystyle{sm}
% \clearpage
% \section*{All About Us}

>>>>

\small{\singlespacing{
\begin{abstract}
Much of international relations scholarship concerns dyads: dyadic hypotheses and especially dyadic data. These types of data do not typically satisfy the conditional independence criterion required for most statistical approaches. Consequently, modeling approaches that fail to adequately capture the data generating process behind dyadic events will suffer from biased coefficients and poorly calibrated standard errors. We introduce a regression-based approach, the Additive and Multiplicative Effects (AME) model, that more fully accounts for the dependencies in dyadic data. First, we conduct a simulation that reveals how the model captures dependencies that emerge in relational data and demonstrate why accounting for these processes improves inference. Second, through replication, we compare the AME model to approaches used in three studies from recent international relations scholarship. For each study, we find that the modeling approach used in the original study performs notably worse at capturing the data generating process compared to the AME. Further, these conventional methods overstate the effect of key variables and underestimate the uncertainty in these effects. In sum, our work shows the consequences of failing to seriously consider dependencies inherent to dyadic data. Perhaps most importantly, by precisely modeling the data generating process underlying political phenomena we improve scholars’ ability to conduct inferential analyses.

\end{abstract}
}}

@@

%\bibliography{/Users/maxgallop/documents/whistle/master}
%\bibliography{/Users/s7m/whistle/master}
 % \bibliography{/Users/mdw/Git/whistle/master}
 \bibliography{/Users/cassydorff/ProjectsGit/master}
% \bibliographystyle{authordate1}
\bibliographystyle{sm}
% \clearpage
% \section*{All About Us}
